### 2014-10-22 paper/include/discussion.tex
corrections

\todo[inline]{Drafty text below!}
\textbf{Broadly compare the techniques from different approaches}

@@

... any of these techniques can be combined with `scheduling real accesses together with refresh ops' (can them???). Mention CREAM as an example.

Another proposed technique is ESKIMO by Isen and John \cite{eskimo}, which focus at reducing total DRAM power through optimizing the accesses to the DRAM. By using one bit of a cache row to denote whether it hold nonsense data, it becomes possible to resolve some memory accesses in the caches, which otherwise would have needed to access DRAM. A memory region is regarded as nonsense if it has been deallocated, or allocated but not written to. The ISA has to be extended to provide the allocation and deallocation information. If a block has to be replaced in a write-through cache and the replaced block is dirty but also deallocated, the cache can ignore writing the replaced block to memory. Similarly, a write miss to a newly allocated area results in a read access that can also be ignored. The latter optimization has support of a structure stored in DRAM which tracks nonsense rows.

The 
Combining ESKIMO with the selective refresh implementation proposed by Oshawa \cite{oshawa} (ESKIMO[31]), $39\%$ of total DRAM power was saved on average.

-Will any approach be benefited / dis-benefited by it?
-Which technique seems future proof?

>>>>

\todo[inline]{Drafty text below!}

\textbf{Mention some smart scheduling techniques}
herpa herpa

CREAM CREAM \cite{cream}

Another proposed technique is ESKIMO by Isen and John \cite{eskimo}, which focus at reducing total DRAM power through optimizing the accesses to the DRAM. By using one bit of a cache row to denote whether it hold nonsense data, it becomes possible to resolve some memory accesses in the caches, which otherwise would have needed to access DRAM. A memory region is regarded as nonsense if it has been deallocated, or allocated but not written to. The ISA has to be extended to provide the allocation and deallocation information. If a block has to be replaced in a write-through cache and the replaced block is dirty but also deallocated, the cache can ignore writing the replaced block to memory. Similarly, a write miss to a newly allocated area results in a read access that can also be ignored. Combining ESKIMO with the selective refresh implementation proposed by Ohsawa \cite{ohsawa} (ESKIMO[31]), $39\%$ of total DRAM power was saved on average.

\textbf{Broadly compare the techniques from different approaches}

@@

... any of these techniques can be combined with `scheduling real accesses together with refresh ops' (can them???)

\textbf{3D stacked DRAM discussion}
-Will any approach be benefited / dis-benefited by it?

-Which technique seems future proof?
